\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}

\lstdefinestyle{code}{basicstyle=\ttfamily\small,breaklines=true,frame=single,columns=fullflexible,showstringspaces=false,keepspaces=true}
\newcommand{\aStar}{a_{\ast}}
\newcommand{\grad}{\nabla}
\newcommand{\diver}{\nabla\!\cdot\!}
\newcommand{\WAIC}{\mathrm{WAIC}}

\title{\bf A Registered Protocol for Testing a Single-Scale Nonlinear Elliptic Gravity Law and a Biological ``Sequention'' Potential}
\author[1]{Henry Arellano}
\affil[1]{Independent Researcher}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We provide a preregistered protocol and reference pipelines for (i) a single-scale, baryons-only nonlinear elliptic gravity law evaluated jointly on galaxy rotation curves and strong lensing; and (ii) an elliptic potential on genotype--phenotype--environment space (Sequention) with preregistered predictive benchmarks. This document includes hypotheses, inclusion criteria, blinding, numerical solvers, uncertainty propagation, pass/fail thresholds, and a step-by-step guide for replication.
\end{abstract}

\section{Hypotheses and Inclusion Criteria}
Physics: (H1) RC median $\chi^2/\nu \le 1.3$; (H2) Lensing median $|\hat{\theta}_E-\theta_E|/\theta_E \le 0.15$ with fixed $\aStar$ and $\mu$; (H3) parsimony vs $\Lambda$CDM+NFW; (H4) $|\gamma-1|<2\times10^{-5}$. Biology: (B1) $\ge$10\% RMSE lift vs GLM/GP with $p<0.01$; (B2) canalization order-invariance within $\pm 5\%$.

\section{Model and Numerics (Physics)}
Solve $\diver[\mu(\|\grad\Phi\|/\aStar)\grad\Phi]=4\pi G\rho_b$ with $\mu(y)=y/(1+y^n)^{1/n}$, $n\in\{1,2,3\}$ chosen once. Finite-volume, uniformly elliptic discretization; nonlinear multigrid with residual drop $\ge 10^8$; fallback Newton--Krylov. Observables: $v_c(r)$ and $\theta_E$ from lensing potential. Bootstrap $N=1024$ for uncertainties.

\section{Model and Numerics (Biology)}
Discrete graph operator with flux $\mu_{\text{bio}}(|\Delta U|/(a^\dagger\Delta))(\Delta U/\Delta)$; optimization by nonlinear CG (Wolfe) + FISTA for group lasso. Baselines: GLM (pairwise + ridge), GP (additive/RBF).

\section{Blinding, Metrics, and Pass/Fail}
Freeze $n$ and calibrate $\aStar$ on a preregistered RC subset; publish config SHA256. Keep lensing labels hidden until predictions are hashed. Metrics: RC $\chi^2/\nu$, lensing fractional error, $\WAIC$/$p_{\text{eff}}$ vs baseline; Solar bound via $|\gamma-1|$.

\section{Step-by-Step Guide}
\begin{enumerate}[leftmargin=2em]
\item Create repo (this skeleton) and commit frozen \texttt{configs/config.json} (hash printed to \texttt{configs/config.hash}).
\item Register on OSF/AsPredicted: paste prereg text from \texttt{physics\_prereg/OSF\_prereg.md} and \texttt{biology\_prereg/OSF\_prereg.md}; add hashes.
\item Run blinded predictions using \texttt{scripts/run\_blinded.sh}; store artifacts in \texttt{results/}.
\item Unblind, compute metrics, and generate \texttt{results/reports/report.md} via \texttt{scripts/make\_audit.sh}.
\item Archive: push to GitHub; create a release; (optionally) mint a DOI via Zenodo.
\end{enumerate}

\bibliographystyle{unsrtnat}
\bibliography{refs}
\end{document}
